Maintenance planning on French military aircraft operations

### 2018-07-05 R/presentations/MOSIM_presentation/presentation.Rmd
MOSIM presentations last modifications

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

@@

* The present model deals with an heterogeneous fleet, with different standards and capacities.
* Multiple objectives have been incorporated in order to satisfy the French Air Force's specific needs.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

@@

* **Try different objective formulations**: availability - maintenability - future state.
* **Break symmetries**: clustering candidates, fixing end availabilities.
* **Add more constraints**: minimal duration of assignments, storage of aircraft.
* **Compare solvers exhaustively**: to determine when each one can be advantageous.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
# exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
# gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

@@

* The present model deals with an heterogeneous fleet, with different standards and capacities.
* Multiple objectives have been incorporated in order to satisfy the French Air Force's specific needs.
* Asignments to missions are done instead of assignments of flight hours.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

@@

* **Add useful cuts**: for example limiting maintenance possibilities.
* **Break symmetries**: clustering candidates, fixing end availabilities.
* **Add more constraints**: minimal duration of assignments, storage of aircraft.
* **Add robustness**: duration of maintenances, new /different missions, unavailable aircraft.
